The Socialization of Meritocracy: The role of the Family and the School

### 2023-06-15 docs/presentacion-effort/presentation-effort.Rmd
ajuste plots

.center[![:scale 100%](images/perc-merit.jpg)]

@@

.pull-right-wide[
.center[![:scale 85%](images/intergetahead.png)]
]

@@

- Family socialisation: parents influence student's perceived meritocracy

>>>>

.center[
![:scale 100%](images/perc-merit.jpg)
]

@@

.pull-right-wide[

.center[![:scale 85%](images/intergetahead1.png)]
]

@@

- Family socialisation: parents positively influence student's perceived meritocracy
